Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-15 main.tex
20180815-2

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Assumption of a PV array}
In this paper, we using following definitions of PV arrays, modules, strings and panels. A PV array formed by several parallel connected PV strings, and string is several series connected PV panels. For a PV panel, formed by two or three PV modules connected in series with bypass diodes. An equivalent connection as showed in Fig. 1.
\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Definition of PV array and internal components.}
\label{fig}
\end{figure}

@@

Furthermore, it is also assumed that for each string it has same number of panels in PV array. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig}
\end{figure}

\section{Reconfiguration Algorithm}
The general steps of reconfiguration algorithm are presented in Fig.2. The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. Afterward, determine real number of working modules \textit{$Q_{MN}$}  per string by applying method in \cite{b10}. Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{MN}$}. Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.  Then grouping panels into different shadow levels. Then grouping panels by different irradiance levels.

After this procedures is conducted for PV array, all panels will be sorted into many groups that from un-shadowed to fully shadowed group. However, if just simply grouping panels by shadow conditions it may cause electrical connection overhead or unable calculate optimal configuration. To further reconfigure PV system into a better configuration, the algorithm will proceed as follow:
\begin{itemize}
\item Sorting group by different irradiance levels, select panels from first group into a PV string which working on high current level.
\item If selected panels' working modules ( \textit{$Q_{MN}^{*}$} ) less than \textit{$Q_{MN}$} , select panels from next irradiance level group.
\item If selected panels' \textit{$Q_{MN}^{*}$} more than \textit{$Q_{MN}$}, re-select panels to adjust \textit{$Q_{MN}^{*}$} equal to \textit{$Q_{MN}$} if it is possible. 
\end{itemize}

When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules \textit{$M_a$} by average MPP voltages \textit{$\bar V_{mpp}$} with $\pm$18\% error \cite{b10}.

@@

%\centerline{\includegraphics{fig1.png}}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{subfigure}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Assumption of a PV array} \label{assum}
In this paper, we using following definitions of PV arrays, modules, strings and panels. A PV array formed by several parallel connected PV strings, and string is several series connected PV panels. For a PV panel, formed by two or three PV modules connected in series with bypass diodes. An equivalent connection as showed in Fig. \ref{fig2}.
\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Definition of PV array and internal components.}
\label{fig2}
\end{figure}

@@

Furthermore, it is also assumed that for each string it has same number of panels in PV array. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig2}
\end{figure}

\section{Reconfiguration Algorithm}
The general steps of reconfiguration algorithm are presented in Fig. \ref{fig2}. The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}. Afterward, determine real number of working modules (\textit{$Q_{M_n}$})  per string by applying method in \cite{b10}. Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}. Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.  Then grouping panels into different shadow distribution.

After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group. However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration. To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
\begin{itemize}
\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
\end{itemize}

\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig3}
\end{figure}

This algorithm will better understood by applying to shadow condition showed in Fig. \ref{fig3}. This PV system is composed with 9 PV panels connected into 3 strings as showed in Fig.\ref{fig3}. Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab}

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab}
\end{center}
\end{table}
The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3). In this example, it is assumed that input range of DC-DC converter and MPPT device defined by \textit{$V_{min}$} = 200V and \textit{$V_{max}$} = 500V. MPP current candidates and MPP voltage candidates are present in ( \ref{e1} ) and ( \ref{e2} ), respectively. Additional, number of real working module at MPP current candidates are given in ( \ref{e3} ).
\begin{equation}
\begin{aligned}
\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$V_{mpp_n}$} = [&12,4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
\end{aligned}
\end{equation}

\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig4}
\end{figure}

Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]. And PV array are organized as Fig \ref{fig4}
Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead. In order to reduce electrical connection simulation time, replacement and feasibility check will be approved.

Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string. Firstly, selecting panels for high current string, string three. According to Table \ref{tab}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A. Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}. Because on extra panel can provide module  working on 3A, no replacement will be approved. Means no further improvement for configuration of string three.
Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized. Selected panels provide 5 modules able to work at 2A, satisfy requirement of \textit{$Q_{M_n}$} $\ge$ 4, but one module more than requirement. The process will replace Panel 4 by Panel 1 that provide just 4 modules working at 2A. Configuration for string two are Panel 8 and Panel 1. At last, select panels for string one. Panel 4, Panel 5, Panel 6 are selected, they can provide 5 modules working at 2A that satisfy requirement. For configuration on string one due to it is the last string to process and meet requirement, in order to reduce computing time replacement will not be approved. Configuration of MPP candidate \{2, 2, 3\} are \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}. As described in section \ref{assum}, each string have identical length and Panel 3 not been used in any configuration. So optimized configuration for this MPP candidate are: \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8, Panel 3\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}. The MPP values of this configuration calculated by multiplay string voltage and current equal to 347.2W are put into evidence.

For the third MPP candidate, as same calculating procedure as fourth MPP candidate, optimized configuration for MPP candidate \{2, 2, 2\} are: \textit{St} 1:\{Panel 4,Panel 8, Panel 3\}, \textit{St} 2: \{Panel 1, Panel 2, Panel 6\}, \textit{St} 3: \{Panel 5, Panel 7, Panel 9\}.

The first MPP candidate \{0.5, 0.5, 2\}, after replacement string three contain four panels, \{Panel 4, Panel 8, Panel 1, Panel 2\} but it is over maximum string length of this PV array.
Also for MPP candidate \{0.5, 2, 2\}, there are no configuration can't provide 7 modules working 
on three different string at 0.5A, 2A, 2A, respectively.

\section{evaluation of optimization algorithm}
%\subsection{Verification of the Proposed algorithm}
This section verifies the effectiveness of proposed algorithm using LTspice simulation. With pilot example presented in last section, first shading scenario as showed in Fig.\ref{fig5a}. To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system. The resulting configuration is depicted in Fig.\ref{fig5b}.

\begin{figure}[htbp]
\begin{minipage}[t]{0.5\linewidth}
\centerline{\includegraphics{fig2.png}}
\caption{(a)}
\label{fig5a}
%\end{minipage}%
%\begin{minipage}[t]{0.5\linewidth}
\centerline{\includegraphics{fig2.png}}
\caption{(b)}
\label{fig5b}
\end{minipage}
\end{figure}

As shown, working module on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized. The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}. It can be seen that after reconfiguration maximum power (!!!!!!!!!! W) are significantly higher than before reconfiguration maximum power (!!!!!!!!W).

\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig6}
\end{figure}
The simulations were performed using an Intel i7-4770 3.2-Ghz processor and 32.0 GB of RAM memory. The calculation time used by the proposed estimation method was 165.2 ms, which is significantly lower than the 57 h, 57 m, and 55 s needed by the exhaustive search algorithm.
\section{conclusions}

%\begin{figure}
%\centering
%\subfigure[the first subfigure]{
%\begin{minipage}[b]{0.2\textwidth}
%\includegraphics[width=1\textwidth]{fig2.png} \\
%\includegraphics[width=1\textwidth]{fig2.png}
%\end{minipage}
%}
%\subfigure[the second subfigure]{
%\begin{minipage}[b]{0.2\textwidth}fig2
%\includegraphics[width=1\textwidth]{fig2.png} \\
%\includegraphics[width=1\textwidth]{fig2.png}
%\end{minipage}
%}
%\end{figure}

%\vspace{100pt}

@@

%\centerline{\includegraphics{fig2.png}}
